Monaural Single-Source Speaker Separation \\ {\large E511 - Signal Processing - Final Project}

### 2018-12-14 paper/main.tex
Updates mostly from Hellen.

\section{Speech Separation Algorithms}
\subsection{KMeans}
The technique of speaker diarization relies on a big pipeline with following steps:
\begin{itemize}
    \item Feature Extraction
    \item Speaker segmentation
    \item Speaker Clustering
    \item Evaluation
\end{itemize}
\subsubsection{Feature Extraction}
In this project, we used 3 approaches to extract features:
\begin{itemize}
    \item A chroma vector (Wikipedia) (FMP, p. 123) is a typically a 12-element feature vector indicating how much energy of each pitch class, {C, C\#, D, D\#, E, ..., B}, is present in the signal. Then use mean of each element as one of input for clustering.
    \item The mel frequency cepstral coefficients (MFCCs) of a signal are a small set of features  which concisely describe the overall shape of a spectral envelope. In this case, mfcc computed 13 MFCCs.The very first MFCC, the 0th coefficient, does not convey information relevant to the overall shape of the spectrum. It only conveys a constant offset, i.e. adding a constant value to the entire spectrum. Therefore, here I discard the first MFCC, then I scale the MFCCs such that each coefficient dimension has zero mean and unit variance.Then use mean of MFCCS as one part of input for clustering.
    \item We divide the audio signal into smaller frames. In smaller time scales audio signals are statistically unchanged. Then for each smaller frames we compute the power spectrum of the signal, and use it as the third part of input for clustering.
\end{itemize}
\subsubsection{Speaker segmentation}\cite{Segmentation} Speaker segmentation which is also known as acoustic change detection aims to detect speaker change such that each contiguous segment corresponds to single speaker only. To find if the two segments correspond to same speaker we have to define some notion of distance metric. In this case, I skipped this step and used the features extrated from above steps as input for kmeans clustering.
\subsubsection{Kmeans Clustering}
Since we knew that the audio from call center is the conversation between 2 speakers(customer service and customer), we set k=2 for kmeans clustering.\\
The results for kmeans speaker diarization are shown in Figure\ref{Fig:speaker diarization 1} and Figure \ref{Fig:speaker diarization 2}.
\begin{figure}[h!]
    \centering  
     \caption{\label{Fig:speaker diarization 1}2 speakers diarization}  
    \includegraphics[width=0.4\textwidth]{kmeans01.png} 
\end{figure}

@@

        Method & SNR \\
        \midrule
        NMF & 0.014 \\
        IRM & 6.380 \\
        cIRM & 15.070 \\
        \midrule
    \end{tabular}

@@

\newline 
% Now we need a bibliography:

>>>>

\section{Speech Separation Algorithms}
\subsection{KMeans}
The technique of speaker diarization relies on a big pipeline with following steps:
\begin{itemize}
    \item Feature Extraction
    \item Speaker segmentation
    \item Speaker Clustering
    \item Evaluation
\end{itemize}
\subsubsection{Feature Extraction}
In this project, we used 3 approaches to extract features:
\begin{itemize}
    \item A chroma vector (Wikipedia) that consists of 12 feature vectors indicating how much energy of each pitch class,In the signal we used the same notation as used i Western music notation, to present every pitch class. Then use mean of each element as one of input for clustering.
    \item MFCCs[Wikipedia] are commonly used as features in speech recognition systems, such as the systems which can automatically recognize numbers spoken into a telephone. In this experiment, mfcc computed 13 MFCCs.The first MFCC does not represent information related to the overall shape of the spectrum. It only contains a constant offset. Therefore, here I discard the first MFCC, then I scale the MFCCs such that each coefficient dimension has zero mean and unit variance.Then use mean of MFCCs as one part of input for clustering.
    \item We divide the audio signal into smaller frames. In smaller time scales audio signals are statistically unchanged. Then for each smaller frames we compute the power spectrum of the signal, and use it as the third part of input for clustering.
\end{itemize}
\subsubsection{Speaker segmentation}\cite{Segmentation} Speaker segmentation is to split an audio stream into smaller segments, so as every segment ideally contains only one speaker. So the key point for speech segment is to find out the change point where speakers changed at that point. For example, in our training data, we have conversation between customer service(speaker 0) and customer(speak 1), so we need to find out each change point speaker 0 to speaker 1 or vice versa. In this case, I skipped this step and used the features extracted from above steps as input for kmeans clustering.
\subsubsection{Kmeans Clustering}
Since we knew that the audio from call center is the conversation between 2 speakers(customer service and customer), we set k=2 for kmeans clustering.\\
The results for kmeans speaker diarization are shown in Figure\ref{Fig:speaker diarization 1} and Figure \ref{Fig:speaker diarization 2}.
\begin{figure}[h!]
    \centering  
     \caption{\label{Fig:speaker diarization 1}2 speakers diarization}  
    \includegraphics[width=0.4\textwidth]{kmeans01.png} 
\end{figure}

@@

        Method & SNR \\
        \midrule
        NMF & 1.924 \\
        IRM & 6.380 \\
        cIRM & 15.070 \\
        \midrule
    \end{tabular}

@@

% Now we need a bibliography:
